---
title: "Lab 02 - Take a sad plot and make it better"
author: "Group Members: Liz, Alfred, Bale, Renee and Jack"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
```

```{r load-data, message = FALSE}
staff <- read_csv("data/instructional-staff.csv")
```


--------

### Exercise 1

_The data frame will have 55 rows because each faculty will have data for 11 years; therefore, 11 * 5 = 55 rows._ 

--------

Team member 2 should pull to download updates and begins here.

### Exercise 2

```{r staff-long-create}
(staff_long <- staff %>%
  pivot_longer(
    cols = - faculty_type, 
    names_to = "year",
    values_to = "percentage"
    ))
```


### Exercise 3
_The guess regarding the number of rows from exercise 1 is correct._

```{r staff-long-inspect}

```


Team member 2 should knit, stage & commit, and push all changes to GitHub.

--------

Team member 3 should pull to download updates and begins here.


### Exercise 4

We can't see any line in the plot.

```{r lineplot-1}
staff_long %>%
  ggplot(aes(x = year, y = percentage, color = faculty_type)) +
  geom_line()

```


### Exercise 5

The part-time faculty increases over the year. The full-time tenure-track faculty and full-time tenure faculty decrease. And graduage student employees and full-time non-tenure-track faculty stay around  20% and 15%.

```{r lineplot-2}
staff_long %>%
   ggplot(aes(x = year, y = percentage, color = faculty_type, group = faculty_type)) +
   geom_point()+geom_line()
```


Team member 3 should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 6

```{r lineplot-3}
staff_long %>%
   ggplot(aes(x = year, y = percentage, color = faculty_type, group = faculty_type)) +
   geom_point()+geom_line()+
   labs(x = "Year",
       y = "Percentage (%)",
       title = "Instructional staff employment trends",
       color = "Faculty Type")
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 7

*Remove this text and add your answer here. No code needed for this exercise!*


### Exercise 8

*Remove this text and add your answer here.*

```{r lineplot-4}
# remove this comment and add your code here
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

All team members should pull to download all updates.


